---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE,
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300
)
devtools::load_all("~/Documents/R/GRSA/ReporterScore/")
library(badger)
```


# TWICE

<!-- badges: start -->
<!-- badges: end -->

A New Enrichment Method for Exposomics: Topology-Weighted Integrated Correlation Enrichment (TWICE) Analysis

The goal of TWiCE is to combine the key strengths of existing approaches:
1. Effectively utilize correlation values, similar to Functional Class Scoring (FCS) methods, so that genes with stronger correlations contribute more to the pathway score.
2. Incorporate pathway topology information, as in Pathway Topology-based (PT) methods, to assign greater weights to biologically important genes such as upstream or highly connected nodes.
In this way, TWiCE bridges the gap between correlation analysis and functional enrichment, providing a more biologically meaningful interpretation of exposome-omics data.

## Installation

You can install the released version of `TWICE` from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("TWICE")
```

You can install the development version of `TWICE` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Asa12138/pcutils")
devtools::install_github("Asa12138/TWICE")
```

## Example

This is a basic example:

```{r example}
library(TWICE)
## basic example code
load_all_pathway_NS() -> all_pathway_NS
# Generate an example data box
cor_df <- data.frame(
  name = all_pathway_NS$name,
  cor = runif(nrow(all_pathway_NS), 0, 1)
)
cor_df <- dplyr::sample_n(cor_df, 200)

calculate_TWICE(all_pathway_NS, cor_df, mode = ) -> res

head(res)


```

